\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{longtable}

\pagestyle{fancy}
\fancyhf{}
\rhead{ChatBox AI – SRS}
\lhead{Software Requirements Specification}
\cfoot{\thepage}

\title{ChatBox AI \\ \Large Software Requirements Specification (SRS)}
\author{Robert Melena, Miguel Aguirre, Robert Guiterrez \\ California State University, Los Angeles}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

%--------------------------------------------------
\section*{Version History}
\addcontentsline{toc}{section}{Version History}

\begin{longtable}{|p{2.5cm}|p{3cm}|p{6cm}|p{3cm}|}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Description} & \textbf{Robert Melena} \\ \hline
1.0 & Snapshot 1 & Initial SRS: core functional and non-functional requirements & Robert Melena, Miguel Aguirre, Robert Guiterrez \\ \hline
1.1 & Snapshot 2 & Requirements for history export and improved onboarding & Robert Melena, Miguel Aguirre, Robert Guiterrez \\ \hline
1.2 & Snapshot 3 & Requirements for multi-channel support and admin metrics & Robert Melena, Miguel Aguirre, Robert Guiterrez \\ \hline
1.3 & Snapshot 4 & Final adjustments and future work & Robert Melena, Miguel Aguirre, Robert Guiterrez \\ \hline
\end{longtable}

\newpage

%==================================================
\section{Introduction}

\subsection{Purpose}
The purpose of this SRS is to define all functional and non-functional requirements for the ChatBox AI system, a web-based AI chat assistant targeted at students seeking help with coursework, planning, and general questions.

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
  \item The course instructor grading the project.
  \item Team members responsible for design, testing, and documentation.
\end{itemize}

\subsection{Product Scope}
ChatBox AI will:
\begin{itemize}
  \item Provide conversational support to students via a web interface.
  \item Store a history of chat sessions for each user.
  \item Offer basic admin tools for monitoring usage.
  \item Integrate with external AI services.
\end{itemize}

%==================================================
\section{Overall Description}

\subsection{User Classes and Characteristics}
\begin{itemize}
  \item \textbf{Student User:} Primary user who chats with the AI. Minimal technical expertise required.
  \item \textbf{Admin User:} Instructor or system administrator who monitors usage statistics and manages configurations.
\end{itemize}

\subsection{Operating Environment}
\begin{itemize}
  \item Web browser (Chrome, Firefox, Edge, etc.).
  \item Backend and database running in Docker containers (Linux-based).
\end{itemize}

\subsection{Design and Implementation Constraints}
\begin{itemize}
  \item For this course, the system is documented but not fully implemented.
  \item Requirements assume use of standard web technologies and a relational database.
\end{itemize}

%==================================================
\section{External Interface Requirements}

\subsection{User Interface}
\begin{itemize}
  \item Responsive chat interface with clear message alignment for user vs.\ AI.
  \item Navigation menu for switching between chat sessions, settings, and admin dashboard.
\end{itemize}

\subsection{Software Interfaces}
\begin{itemize}
  \item RESTful API endpoints for chat messages, user management, and admin analytics.
  \item External AI provider API (abstracted by the AI Adapter).
  \item Database interface (e.g., PostgreSQL driver).
\end{itemize}

%==================================================
\section{Functional Requirements}

\subsection{User Registration and Login}
\begin{itemize}
  \item \textbf{FR1:} The system shall allow users to create an account using email and password.
  \item \textbf{FR2:} The system shall authenticate users using their credentials.
\end{itemize}

\subsection{Chat Sessions}
\begin{itemize}
  \item \textbf{FR3:} The system shall allow users to start a new chat session.
  \item \textbf{FR4:} The system shall store each message in a chat session.
  \item \textbf{FR5:} The system shall allow users to revisit previous chat sessions.
  \item \textbf{FR6 (Snapshot 2):} The system shall allow users to export a chat session as a text or PDF file.
\end{itemize}

\subsection{AI Responses}
\begin{itemize}
  \item \textbf{FR7:} The system shall send user messages to an AI provider and display the AI response.
  \item \textbf{FR8:} The system shall handle AI timeouts and display appropriate error messages.
\end{itemize}

\subsection{Admin Features}
\begin{itemize}
  \item \textbf{FR9 (Snapshot 3):} The system shall provide an admin dashboard with basic usage statistics (number of users, number of sessions, total messages).
  \item \textbf{FR10 (Snapshot 3):} The system shall allow admin users to view aggregated metrics by date range.
\end{itemize}

%==================================================
\section{Non-Functional Requirements}

\subsection{Performance Requirements}
\begin{itemize}
  \item \textbf{NFR1:} The system should respond to user requests within a few seconds, excluding AI provider delays.
  \item \textbf{NFR2:} The system should support multiple concurrent users in a typical university-scale setting.
\end{itemize}

\subsection{Security Requirements}
\begin{itemize}
  \item \textbf{NFR3:} Passwords must never be stored in plain text.
  \item \textbf{NFR4:} Only authenticated users can access their own chat history.
  \item \textbf{NFR5:} Admin-only features must be protected by role-based access control.
\end{itemize}

\subsection{Reliability, Availability, and Maintainability}
\begin{itemize}
  \item \textbf{NFR6:} The system should be designed so that services can be restarted independently using Docker.
  \item \textbf{NFR7:} Logs should be kept for diagnostic purposes.
\end{itemize}

%==================================================
\section{Legal and Ethical Considerations}

\subsection{User Data and Privacy}
\begin{itemize}
  \item The system should minimize the collection of personally identifiable information.
  \item Users should be informed that their conversation data may be stored and used to improve the system.
\end{itemize}

\subsection{Academic Integrity}
\begin{itemize}
  \item ChatBox AI could be misused to generate answers for assignments or exams.
  \item The user interface should include a disclaimer reminding students to use AI assistance responsibly and align with university academic integrity policies.
\end{itemize}

%==================================================
\section{Glossary}

\begin{description}
  \item[Student User] A typical student using the chat interface.
  \item[Admin User] Instructor or system administrator.
  \item[Chat Session] A collection of messages between a user and the AI.
\end{description}

\end{document}
