\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}

\title{ChatBox AI \\ \Large Snapshot Objectives}
\author{Your Name}
\date{\today}

\begin{document}
\maketitle

\section{Snapshot 1 – Start}
\subsection*{Goals}
\begin{itemize}
  \item Define the overall vision and scope of ChatBox AI.
  \item Draft initial versions of the SDD and SRS.
  \item Design the high-level architecture and workflow diagram.
  \item Set up Jira project and initial epics and tasks.
\end{itemize}

\section{Snapshot 2 – Checkpoint 1}
\subsection*{Reflection}
\begin{itemize}
  \item Core architecture and requirements documented.
  \item Initial UI and data model descriptions drafted.
\end{itemize}

\subsection*{New Objectives}
\begin{itemize}
  \item Add large feature: \textbf{Conversation History Export}.
  \item Update SDD and SRS to include export functionality.
  \item Create and document TestRail test cases for login, chat, and export.
  \item Update workflow diagram to include export path.
\end{itemize}

\section{Snapshot 3 – Checkpoint 2}
\subsection*{Reflection}
\begin{itemize}
  \item Export feature documented and integrated into design.
  \item Initial TestRail runs documented for Snapshot 2.
\end{itemize}

\subsection*{New Objectives}
\begin{itemize}
  \item Add large feature: \textbf{Admin Metrics Dashboard}.
  \item Update SDD, SRS, and design spec for admin views and metrics.
  \item Add new TestRail test cases for admin endpoints and dashboard.
  \item Refine Docker design to include monitoring/logging component (conceptual).
\end{itemize}

\section{Snapshot 4 – Due Date}
\subsection*{Reflection}
\begin{itemize}
  \item Core features (chat, history, export, admin metrics) are fully documented.
  \item All documents (SDD, SRS, user manual, design spec) updated to final versions.
\end{itemize}

\subsection*{Future Work}
\begin{itemize}
  \item Personalization of AI responses per user.
  \item Integration with learning management systems.
  \item Mobile app version of ChatBox AI.
\end{itemize}

\end{document}
